Technical Report

### 2018-06-22 fully-abstract-comp/technical-report.tex
Simplify lemma and proof.

\begin{lemma}[Untrusted source values are reasonable]
  \label{lem:untrusted-source-values-are-reasonable}
  If
  \begin{itemize}
  \item $\gc = (\ta,\stkb,\gsigrets,\gsigcloss)$
  \item $\npair{(w,\_)} \in \lrv(W_w)$
  \item $\memSat{\ms_S,\stk,\ms_\stk,\_}{W_M}$
  \item $\purePart{W_w} \oplus \purePart{W_M}$ is defined
  \item $\pwheap[W_w](r_\code) \nequal \codereg{\sigrets,\sigcloss,\code,\gc}$
  \item $\dom(\code) \subseteq \ta$
  \item $\sigrets \subseteq \gsigrets$ and $\sigcloss \subseteq \gsigcloss$
  \end{itemize}
  then, with respect to $\code,\ta,\gsigrets,\gsigcloss$, $w$ is reasonable up to $n$ steps in memory $\ms_S$ and free stack $\ms_\stk$.
\end{lemma}
\begin{proof}
  Induction over $n$.
  For $n=0$ all words are reasonable.
  For $n>0$, we need to prove four implications:
  \begin{itemize}
  \item If $w = \seal{\sigma_\baddr,\sigma_\eaddr,\_}$, then $[\sigma_\baddr,\sigma_\eaddr] \mathrel{\#} (\gsigrets \cup \gsigcloss)$:

    This follows directly from $\npair{(w,\_)} \in \lrv(W_w)$ by definition of $\lrv$.
    % Take $\sigma \in [\sigma_b,\sigma_e]$, we need to prove that $\sigma \not\in (\gsigrets \cup \gsigcloss)$.
    % Assume that $\sigma \in (\sigrets \cup \sigcloss)$ and we will prove a contradiction.

    % From $\npair{(w,\_)} \in \lrv(W_w)$, we get a $r \in \dom(\pwheap[W_w])$ such that $\pwheap[W_w](r) = (\pure,\_,H_\sigma)$ and $H_\sigma~\sigma \nequal \lrv$.

    % From $\memSat{\ms_S,\stk,\ms_\stk,\_}{W_M}$, it follows that $\npair{(\overline{\sigma},\_,\_)} \in \lrheap(\pwheap[W_M])(W_{\var{heap}})$ for some $\overline{\sigma}$, $W_{\var{heap}}$ with $W_M = W_{\var{stack}} \oplus W_{\var{free\_stack}} \oplus W_{\var{heap}}$.

    % From this, it follows that there exists a $R_\var{seal} : \dom(\activeReg{\pwheap[W_{\var{heap}}]}) \fun \powerset{\Seal}$, $\biguplus_{r \in \dom(\activeReg{\pwheap[W_{\var{heap}}]})} R_\var{seal}(r)) \subseteq \overline{\sigma}$ and $\dom(\pwheap[W_{\var{heap}}](r).H_\sigma) = R_\var{seal}(r)$ for all $r$.

    % From $\dom(\pwheap[W_{\var{heap}}](r).H_\sigma) = R_\var{seal}(r)$ and the definedness of all the $\oplus$ operations on worlds, it follows that also $\dom(\pwheap[W_w](r).H_\sigma) = R_\var{seal}(r)$ for all $r$.

    % From the facts that $\pwheap[W_w](r_\code) \nequal \codereg{\sigrets,\sigcloss,\code,(\ta,\stkb)}$, $\pwheap[W_w].H_\sigma~\sigma \nequal \lrv$, the disjointness of all the $R_{\var{seal}}(r)$, it follows that $r = r_\code$.
    % However, this contradicts Lemma~\ref{lem:codereg-Hsigma-not-lrv}.

@@

    By $\npair{(w,\_)} \in \lrv(W_w)$, we get some region $r \in \dom(\pwheap)$ and a set of return seals, a set of closure seals and a code memory: $\sigrets',\sigcloss',\mscode'$ such that $\pwheap(r) = (\pure,\_,H_\sigma)$ and $H_\sigma \nequal H^\mathrm{code,\square}_\sigma \; \sigrets' \; \sigcloss' \; \mscode' \; \gc)$ and $\npair[n']{(\sealed{\sigma,\vsc},\_)} \in H_\sigma \; \sigma \; \xi^{-1}(W)$ for all $n' < n$, so in particular for $n' = n-1$.
    It follows easily from the above that also $\npair[n-1]{(\vsc,\_)} \in H^\mathrm{code,\square}_\sigma \; \sigrets' \; \sigcloss' \; \mscode' \; \gc \; \sigma \; \xi^{-1}(W)$.

    It also follows from $\memSat{\ms_S,\stk,\ms_\stk,\_}{W_M}$, $\sigma \not\in (\gsigrets\cup \gsigcloss)$ and $\sigrets \subseteq \gsigrets$ and $\sigcloss \subseteq \gsigcloss$ that $\sigrets \uplus \sigcloss \# \sigrets' \uplus \sigcloss'$.

    This gives us three cases for $\vsc$.
    The two first cases $\vsc = \retptrd(\_,\_)$ and $\vsc = \retptrc(\_,\_,\_)$ are easily discharged as the reasonability definition puts no requirements on return pointers.
    For the final case, $\sigma \in \sigcloss'$ and either
    \begin{itemize}
    \item $\dom(\code') \mathrel{\#} \ta \tand \npair[n-1]{(\vsc,\_)} \in \lrv (W)$; or
    \item $\dom(\code') \subseteq \ta$, $\sigcloss' \subseteq \gsigcloss$, and $\npair{(\vsc,\_)} \in \lrvg{\trust}(W)$ for $\trust = \untrusted$ iff $\nonExec{\vsc}$.
    \end{itemize}
    In the first case, the result follows from the induction hypothesis.
    In the second case, we have a contradiction with $\sigma \not\in (\gsigrets\cup \gsigcloss)$.

@@

      Which follows by definition of $\purePart{}$ and the fact that $R_W'(a)$ is $W_M$ with part of its ownership, but $\purePart{}$ strips away the ownership making the two compatible.
    \item $\pwheap[W_w](r_\code) \nequal[n-1] \codereg{\sigrets,\sigcloss,\code,\gc}$

      By property of $n$-equality.
    \item $\dom(\code) \subseteq \ta$ and $\sigrets \subseteq \gsigrets$ and $\sigcloss \subseteq \gsigcloss$ and $\gc = (\ta,\stkb,\gsigrets,\gsigcloss)$

      Follows by assumption.
    \end{itemize}
    which gives us that, with respect to $\code,\ta,\gsigrets,\gsigcloss$, $\pi_1(R_\ms(r))(a)$ is reasonable up to $n-1$ steps in memory $\ms_S$ and free stack $\ms_\stk$.
    Which is what we wanted as $\pi_1(R_\ms(r))(a) = \ms_S(a)$.

@@

      Which follows by definition of $\purePart{}$ and the fact that $R_W'(a)$ is $W_M$ with part of its ownership, but $\purePart{}$ strips away the ownership making the two compatible.
    \item $\pwheap[W_w](r_\code) \nequal[n-1] \codereg{\sigrets,\sigcloss,\code,\gc}$

      By property of $n$-equality.
    \item $\dom(\code) \subseteq \ta$ and $\sigrets \subseteq \gsigrets$ and $\sigcloss \subseteq \gsigcloss$ and $\gc = (\ta,\stkb,\gsigrets,\gsigcloss)$

      Follows by assumption.
    \end{itemize}
    which gives us that, with respect to $\code,\ta,\gsigrets,\gsigcloss$, $\pi_1(R_\ms(r))(a)$ is reasonable up to $n-1$ steps in memory $\ms_S$ and free stack $\ms_\stk$.
    Which is what we wanted as $\pi_1(R_\ms(r))(a) = \ms_\stk(a)$.
  \end{itemize}
\end{proof}

>>>>

\begin{lemma}[Untrusted source values are reasonable]
  \label{lem:untrusted-source-values-are-reasonable}
  If
  \begin{itemize}
  \item $\gc = (\ta,\stkb,\gsigrets,\gsigcloss)$
  \item $\npair{(w,\_)} \in \lrv(W_w)$
  \item $\memSat{\ms_S,\stk,\ms_\stk,\_}{W_M}$
  \item $\purePart{W_w} \oplus \purePart{W_M}$ is defined
  \end{itemize}
  then, with respect to $\ta,\gsigrets,\gsigcloss$, $w$ is reasonable up to $n$ steps in memory $\ms_S$ and free stack $\ms_\stk$.
\end{lemma}
\begin{proof}
  Induction over $n$.
  For $n=0$ all words are reasonable.
  For $n>0$, we need to prove four implications:
  \begin{itemize}
  \item If $w = \seal{\sigma_\baddr,\sigma_\eaddr,\_}$, then $[\sigma_\baddr,\sigma_\eaddr] \mathrel{\#} (\gsigrets \cup \gsigcloss)$:

    This follows directly from $\npair{(w,\_)} \in \lrv(W_w)$ by definition of $\lrv$.

@@

    By $\npair{(w,\_)} \in \lrv(W_w)$, we get some region $r \in \dom(\pwheap)$ and a set of return seals, a set of closure seals and a code memory: $\sigrets,\sigcloss,\mscode$ such that $\pwheap(r) = (\pure,\_,H_\sigma)$ and $H_\sigma \nequal H^\mathrm{code,\square}_\sigma \; \sigrets \; \sigcloss \; \mscode \; \gc)$ and $\npair[n']{(\sealed{\sigma,\vsc},\_)} \in H_\sigma \; \sigma \; \xi^{-1}(W)$ for all $n' < n$, so in particular for $n' = n-1$.
    It follows easily from the above that also $\npair[n-1]{(\vsc,\_)} \in H^\mathrm{code,\square}_\sigma \; \sigrets \; \sigcloss \; \mscode \; \gc \; \sigma \; \xi^{-1}(W)$.

    This gives us three cases for $\vsc$.
    The two first cases $\vsc = \retptrd(\_,\_)$ and $\vsc = \retptrc(\_,\_,\_)$ are easily discharged as the reasonability definition puts no requirements on return pointers.
    For the final case, $\sigma \in \sigcloss$ and either
    \begin{itemize}
    \item $\dom(\mscode) \mathrel{\#} \ta \tand \npair[n-1]{(\vsc,\_)} \in \lrv (W)$; or
    \item $\dom(\mscode) \subseteq \ta$, $\sigcloss \subseteq \gsigcloss$, and $\npair{(\vsc,\_)} \in \lrvg{\trust}(W)$ for $\trust = \untrusted$ iff $\nonExec{\vsc}$.
    \end{itemize}
    In the first case, the result follows from the induction hypothesis.
    In the second case, we have a contradiction with $\sigma \not\in (\gsigrets\cup \gsigcloss)$.

@@

      Which follows by definition of $\purePart{}$ and the fact that $R_W'(a)$ is $W_M$ with part of its ownership, but $\purePart{}$ strips away the ownership making the two compatible.
    \end{itemize}
    which gives us that, with respect to $\ta,\gsigrets,\gsigcloss$, $\pi_1(R_\ms(r))(a)$ is reasonable up to $n-1$ steps in memory $\ms_S$ and free stack $\ms_\stk$.
    Which is what we wanted as $\pi_1(R_\ms(r))(a) = \ms_S(a)$.

@@

      Which follows by definition of $\purePart{}$ and the fact that $R_W'(a)$ is $W_M$ with part of its ownership, but $\purePart{}$ strips away the ownership making the two compatible.
    \end{itemize}
    which gives us that, with respect to $\ta,\gsigrets,\gsigcloss$, $\pi_1(R_\ms(r))(a)$ is reasonable up to $n-1$ steps in memory $\ms_S$ and free stack $\ms_\stk$.
    Which is what we wanted as $\pi_1(R_\ms(r))(a) = \ms_\stk(a)$.
  \end{itemize}
\end{proof}
